\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}

% 汎用的なフォントパッケージ
\usepackage[T1]{fontenc}
\usepackage{lmodern} 

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\setlength{\footskip}{10pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% 余白の最適化
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% --- 見出し（section）をゴシック・太字にし、下線を引く ---
\titleformat{\section}{
  \sffamily\Large\bfseries\vspace{3pt}
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

% --- 小見出し（subsection）もゴシック・太字にする ---
\titleformat{\subsection}{
  \sffamily\large\bfseries\vspace{2pt}
}{}{0em}{}

\newcommand{\resumeItem}[1]{
  \item{
    {#1 \vspace{-4pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

%-----------HEADER-----------
\begin{center}
    {\sffamily\Huge\bfseries Ruri Sase} \\ \vspace{5pt}
    \small{School of Engineering, Kochi University of Technology} \\
    \small{E-mail: \href{mailto:296005z@gs.kochi-tech.ac.jp}{\color{blue}296005z@gs.kochi-tech.ac.jp} $|$ Web: \href{https://ruri-s.github.io/}{\color{blue}https://ruri-s.github.io/}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {Doctoral student in Civil engineering}{Apr. 2025 -- Present}
      {Kochi University of Technology (Supervisor: Prof. Satoshi Sugiura)}{Kochi, Japan}
    \resumeSubheading
      {M.S. in Civil engineering}{Apr. 2023 -- Mar. 2025}
      {Hokkaido University (Supervisor: Prof. Satoshi Sugiura)}{Hokkaido, Japan}
    \resumeSubheading
      {B.S. in Civil engineering}{Apr. 2019 -- Mar. 2023}
      {Hokkaido University}{Hokkaido, Japan}
\resumeSubHeadingListEnd

%-----------APPOINTMENTS-----------
\section{Appointments}
\resumeSubHeadingListStart
    \resumeSubheading
      {Research Fellowship for Young Scientist (DC1)}{Apr. 2025 -- Present}
      {Japan Society for the Promotion of Science (JSPS)}{}
\resumeSubHeadingListEnd

%-----------RESEARCH AREAS-----------
\section{Research Keywords}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    transportation network analysis, connectivity, graph theory, optimization
    }}
\end{itemize}

%-----------PUBLICATIONS-----------
\section{Publications}

\subsection*{Journal Articles}
\begin{enumerate}[leftmargin=0.3in, label=\arabic*.]
    \small{
    \item Ruri Sase, Satoshi Sugiura, Empirical analysis of cut-based approach for screen-line traffic counting location problem with pre-installed sensors, \textit{International Journal of Intelligent Transportation Systems Research}, 2025.
    \item Ruri Sase, Satoshi Sugiura, and Anthony Chen, Optimized graph-cut approach for the screen-line traffic counting location problem: An exact and efficient solution method, \textit{Expert Systems with Applications}, 2025.
    \item Ruri Sase, Satoshi Sugiura, Inbound traffic capture link-design problem independent of assumptions on users’ route choices, \textit{EURO Journal on Transportation and Logistics}, 2024.
    }
\end{enumerate}

\subsection*{Preprints}
\begin{enumerate}[leftmargin=0.3in, label=\arabic*.]
    \small{
    \item Ruri Sase, Satoshi Sugiura and Fumitaka Kurauchi, A novel zone-cut-based network representation framework for a robust origin-destination trip matrix estimation, 2026.
    }
\end{enumerate}

%-----------CONFERENCE PRESENTATIONS-----------
\section{Conference Presentations}
\subsection*{International Conference Presentations}
\begin{enumerate}[leftmargin=0.3in, label=\arabic*.]
    \small{
    \item Toshiki Arai, Ruri Sase, Satoshi Sugiura, Hiroaki Nishiuchi: The screen-line traffic counting location problem under observation uncertainty, \textit{12th International Symposium on Travel Demand Management (TDM)}, Sydney, Australia, December 2025.
    \item Ruri Sase, Satoshi Sugiura, Fumitaka Kurauchi: Zone-cut based approach for path-independent OD trip matrix estimation, \textit{12th International Symposium on Travel Demand Management (TDM)}, Sydney, Australia, December 2025.
    \item Ruri Sase, Satoshi Sugiura: Excess-demand isolation vulnerability analysis based on a bipartitioning minimum cut, \textit{The 12th Triennial Symposium on Transportation Analysis conference (TRISTAN)}, Okinawa, Japan, June 2025.
    \item Ruri Sase, Satoshi Sugiura: O/D cut optimization for traffic sensor location problem, \textit{The 27th International Conference of Hong Kong Society for Transportation Studies (HKSTS)}, Hong Kong, December 2023.
    \item Ruri Sase, Satoshi Sugiura: Inflow Traffic to a Specific Community Capturing Link Design Problem Independent of User Routing Assumptions, \textit{The 15th international conference of the eastern asia society for transportation studies (EASTS)}, Shah Alam, Malaysia, September 2023.
    }
\end{enumerate}

\subsection*{Non-Refereed Conference Presentations in Japanese}
\begin{enumerate}[leftmargin=0.3in, label=\arabic*.]
    \small{
    \item Ruri Sase, Satoshi Sugiura: Empirical analysis of cut-based approach for screen-line traffic counting location problem with pre-installed sensors, \textit{23rd ITS Symposium 2025}, International Conference Center Hiroshima, Hiroshima, Japan, December 2025.
    \item Ruri Sase, Satoshi Sugiura: Analysis of link traffic counting location on actual road networks based on screen-line traffic counting location problem, \textit{The 71st JSCE Conference of Infrastructure Planning and Management}, Kagawa University, Kagawa, Japan, June 2025.
    \item Kyo Fujita, Satoshi Sugiura, Ruri Sase: Analysis of the effect of transport network improvement on the optimal road restoration design problem to minimise cumulative isolated duration, \textit{The 71st JSCE Conference of Infrastructure Planning and Management}, Kagawa University, Kagawa, Japan, June 2025.
    \item Ruri Sase, Satoshi Sugiura, Fumitaka Kurauchi: Zone-cut based OD trip table estimation with vehicle trajectories, \textit{The 70th JSCE Conference of Infrastructure Planning and Management }, Okayama University, Okayama, Japan, November 2024.
    \item Ruri Sase, Satoshi Sugiura: Location-based vulnerability analysis: Identifying critical links that cause simultanious isolation, \textit{The 69th JSCE Conference of Infrastructure Planning and Management}, Hokkaido University, Hokkaido, Japan, May 2024.
    \item Satoshi Sugiura, Ruri Sase: Road network restoration optimization problem to minimize cumulative isolated days \textit{The 69th JSCE Conference of Infrastructure Planning and Management}, Hokkaido University, Hokkaido, Japan, May 2024.
    \item Ruri Sase, Satoshi Sugiura: Day-to-day O/D trip estimation based on road network topology and observable traﬃc flow data, \textit{The 68th JSCE Conference of Infrastructure Planning and Management}, Tokyo Metropolitan University, Tokyo, Japan, November 2023.
    \item Ruri Sase, Satoshi Sugiura: Inflow traffic capturing link design problem to specific communities independent of route choice assumptions, \textit{Japan Society of Civil Engineers Hokkaido Branch 2022 Annual Meeting}, Sapporo, Hokkaido, Japan, January 2023.
    }
\end{enumerate}

%-----------GRANTS AND AWARDS-----------
\section{Grants and Awards}
\subsection*{Grants and Fellowships}
\resumeSubHeadingListStart
    \resumeSubheading
    {JSPS Grant-in-Aid for JSPS Research Fellows (25KJ2046)}{2025 -- Present}
    {JSPS KAKENHI (Principal Investigator)}{}
    \resumeSubheading
    {Repayment Exemption for Particularly Outstanding Achievement (Full Exemption)}{Jul. 2025}
    {Japan Student Services Organization (JASSO)}{}
    \resumeSubheading
    {Hokkaido University Mirai IT Talent Scholarship}{Apr. 2024 -- Mar. 2025}
    {NITORI International Scholarship Foundation, Japan}{}
\resumeSubHeadingListEnd

\subsection*{Awards}
\resumeSubHeadingListStart
    \resumeSubheading
    {Best Poster Award}{Dec. 2025}
    {23rd ITS Symposium 2025, ITS Japan, Japan}{}
    \resumeSubheading
    {Encouragement Research Award for Students, The 7th Re-design Research Award}{Dec. 2025}
    {Urban Re-design Studies Unit, Japan}{}
    \resumeSubheading
    {Best Master's Student Award in Civil Engineering}{Mar. 2025}
    {Division of Engineering and Policy for Sustainable Environment, Hokkaido University, Japan}{}
    \resumeSubheading
    {Outstanding Poster Award}{May 2024}
    {JSCE Committee on Infrastructure Planning and Management, Japan}{}
\resumeSubHeadingListEnd

\end{document}